New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems\tnoteref{t1}

### 2020-08-11 paper/answer_rev_2.tex
wip

		\section*{Answer to reviewer \# 2}
		First, thanks for dedicating your time to revise our work. We found every one of the points made of great importance for us to achieve a top quality paper.

		Following we provide answers to each one of the comments you have given us:

		\textbf{Comment \#1:} `` The highlights (contributions of the paper) and organization of the remaining sections should be presented at the end of Section 1."

		We address this issued by adding a paragraph to the end of our Introduction:

@@

		This paragraph can be found in the manuscript in pages 3 and 4.

@@

		We agree that using ``fixed shape" without clearly defining what it is can be confusing to the reader. To address this issue we rewrote the pieces of text where this was being used:
		\begin{itemize}
			\item In the first paragraph of the abstract (page 2), we used the term ``given their major and minor axis" to better convey the same idea.

@@

		We address this issued by adding a new paragraph to our Introduction citing the work ``\textit{Mustafa S. Canbolat and Michael von Massow. Planar maximal covering with ellipses.}", which covers with great detail the practical applications of the problems studied in our work:

@@

		This issued is addressed in the Introduction section on page 2. We agree with you that the literature review needed improvement, and we believe that we were able to improve on that regard with the following changes:

@@

	Now, after these additions, the piece of our Introduction doing literature review of PMCLP is as follows:

@@

	We did consider the list of suggested works we could look at to improve our literature review you have given us, however, even though we think they are great suggestions, we decided to cite two works we were more familiar with, also with the intention of not extending this part of the Introduction too much.
	It is worth mentioning though, that some works of Daoqin Tong are cited in the survey paper we are using.

@@

		``We were able to run experiments with up to 700 demand points; however, it is clear that the number of ellipses is the critical parameter of both algorithms, as even for small demand sets, we could not go over 7 ellipses."

@@

		Thanks for this comment, we, too, think that depending on the viewpoint, considering the weight of each point to be a function which depends on the set of ellipses covering is more natural. We believe that our methods could be trivially adapted to work with this different definition, however, we also think that we have to ponder about doing this change because this is not the traditional definition of any other PMCLP we have based our developments on; meaning that we would have to have a strong motive for this not to look like an arbitrary change.

@@

		The way our methods work is to look for solutions with points on the ellipses, this type of solution is not favorable when we have this constraint as, for example, see the counter-example in this figure:

@@

		It is possible to see that there are non-overlapping solutions, however, our algorithm would fail to find any. Notice that moving the ellipse with no points on its coverage region's border in order to put at least two points on it would cause overlap.

		We believe methods for the problems with this additional constraint would have to come from a different base idea than ours do.

>>>>

		\section*{Answer to reviewer \# 2}
		Thanks a lot for dedicating your time to revise our work. We found every one of your comments very helpful and insightful, and we believe that after taking them into account our work has much improved.

		Following we provide replies to each one of the comments you have given us:

		\textbf{Comment \#1:} ``The highlights (contributions of the paper) and organization of the remaining sections should be presented at the end of Section 1."

		We addressed this issued by adding a paragraph to the end of our Introduction:

@@

		This paragraph can be found in the manuscript in pages 3 and 4.
		\\

@@

		Thanks for the great observation; we agree that it is not very clear what the term 'fixed shape' ellipses means, and decided to rewrite the text everywhere it appeared. Please find below the changes we have made:
		\begin{itemize}
			\item In the first paragraph of the abstract (page 2), we used the term ``given their major and minor axis" to better convey the same idea.

@@

		Thanks for the comment, we addressed this issued by adding a new paragraph to our Introduction citing the work ``\textit{Mustafa S. Canbolat and Michael von Massow. Planar maximal covering with ellipses.}", which covers with great detail the practical applications of the problems studied in our work:

@@

		Thanks for all the great suggestions, after pondering about it, we agree that our literature review needed work, thanks for pointing it out.
		We spent some time on trying to improve it, in summary, those are the changes we have made to our introduction:

@@

	After these additions, the piece of our Introduction doing literature review of PMCLP is as follows:

@@

	We did consider the list of works you gave us as suggestions, however, even though we think they are great papers, we decided to cite two works we were more familiar with. It is worth mentioning though, that some works of Daoqin Tong are cited in the survey paper we are using.
\\

@@

		``We were able to run experiments with up to 700 demand points; however, it is clear that the number of ellipses is the critical parameter of both algorithms, as even for small demand sets, we could not go over 7 ellipses."
		\\

@@

		Thanks for this comment, we, too, think that depending on the viewpoint, considering the weight of each point to be a function which depends on the set of ellipses covering it is more natural. We believe that our methods could be trivially adapted to work with this different definition, however, we also think that we have to ponder about doing this change because this is not the traditional definition of any other PMCLP we have based our developments on; meaning that we would have to have a strong motive for this not to look like an arbitrary change.
		\\

@@

		We also produced an example to show you what would happen if we simply added this constraint without changing anything to our method. 
		The way our algorithms work is that it looks for solutions with points on the ellipses. This type of solution is not favorable when we have this constraint as, for example, see the counter-example in this figure:

@@

		The solution shown is non-overlapping -- actually there are an infinite number of non-overlapping equivalent solutions --, however, our algorithm would fail to find any equivalent solution. Notice that moving the ellipse with no points on its coverage region's border in order to put at least two points on it would cause overlap.
		We believe methods for the problems with this additional constraint would have to come from a different basis.
